Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-09 paper.qmd
Added tourr and detourr references

The new methodology is accompanied by an R package called quollr, so that it is readily usable and broadly accessible. The package has methods to fit the model, compute diagnostics and also visualise the results, with interactivity. We have primarily used the langevitour software [@harisson2024] to view the model in the data space, but other tour software such as tourr [@tourr] and [@detourr] could be also used.

>>>>

The new methodology is accompanied by an R package called quollr, so that it is readily usable and broadly accessible. The package has methods to fit the model, compute diagnostics and also visualise the results, with interactivity. We have primarily used the langevitour software [@harisson2024] to view the model in the data space, but other tour software such as tourr [@wickham2011] and detourr [@hart2022] could be also used.
